Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2016-10-31 jssst/paper.tex
Modify RiteVM Tasks to RiteVMs
Final version

\subsection{Synchronization of Multiple RiteVM Tasks}

 \begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
\caption{Synchronization of multiple RiteVM tasks}
\label{fig:eval_synchronization}
\end{figure}

To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
It was confirmed that the time was within the theoretical value. Theoretical value is 
\begin{displaymath}
    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1).}
\end{displaymath}
Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
Note that the periodic time is 1 msec.
As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.

@@

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        ChaiScript \cite{url:ChaiScript}             &            &            &            &    -       &    -        &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

Open-source runtime systems for scripting languages have been proposed previously such python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, ChaiScript\cite{url:ChaiScript}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

\section{Actual Results}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework stood second in a regional competition.

>>>>

\subsection{Synchronization of Multiple RiteVMs}

 \begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
\caption{Synchronization of multiple RiteVMs}
\label{fig:eval_synchronization}
\end{figure}

To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
It was confirmed that the time was within the theoretical value which is 
\begin{displaymath}
    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1).}
\end{displaymath}
Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
Note that the periodic time is 1 msec.
As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.

@@

\begin{table*}[t]
    \caption{Comparison of proposed and previous methods}
    \label{tab:comparison}
    \begin{center}
    {\tabcolsep=0.05cm
    \begin{tabular}{c||c|cccccc}
        & \shortstack{Bluetooth\\Loader}
        & \shortstack{Call\\C Function} 
        & \shortstack{Legacy Code of\\Embedded System} 
        & \shortstack{VM\\Management} 
        & \shortstack{VM\\Scheduler} 
        & \shortstack{Synchronization\\of Applications} \\ \hline
        ChaiScript \cite{url:ChaiScript}             &            &            &            &            &             &            \\
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            \\
        Squirrel \cite{url:Squirrel}                 &            & \checkmark &            &            &             &            \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark \\
    \end{tabular}
    }
    \end{center}
\end{table*}

Open-source runtime systems for scripting languages have been proposed such as ChaiScript\cite{url:ChaiScript}, python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, Squirrel \cite{url:Squirrel}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

\section{Practical Use}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework stood second in a regional competition.
